Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-27 ms.tex
searching theory revised

The area that a male $m$ with speed trait $v$ and radius trait $r$ can search in time step $dt$ is
\begin{equation}
    A_{searched} = 2r \cdot v \cdot dt
\end{equation}
See Fig. \ref{fig:area searched}.

We let the total area enclosing all males and all nests be a parameter, $A_{total}$.

The probability of a male that covers $A_{searched}$ area in time period $dt$ encountering any nest is:
\begin{equation}
    P(\rm {discovery}) = \frac {N \cdot A_{searched}} {A_{total}}
\end{equation}
\citep{Gillespie-1976}
The energy used by a male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.

>>>>

The area that a male $m$ with speed trait $v$ and radius trait $r$ can search in one time step is
\begin{equation}
    2r \cdot v
\end{equation}
See Fig. \ref{fig:area searched}.

We let the total area enclosing all males and all nests be a parameter, $A_{total}$. We assume spatially random nests.

The mean encounter rate $\varepsilon$ is:
\begin{equation} \label{eq:encounter rate}
    \varepsilon = \frac {N \cdot 2r\cdot v} {A_{total}}
\end{equation}
\citep{Gurarie2012}

We then use this as the rate parameter $lambda$ to repeatedly draw the time of the next discovery event for this individual from the exponential distribution, we do this for each male from when they mature up to when the females matrure.

When an event occurs we select a nest randomly and then the male will either occupy it or contest another male for it.

%I think I might use a priority queue for this...

The energy used by a male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.
